Resolving the measurement uncertainty paradox in ecological management

### 2018-12-28 manuscripts/manuscript.tex
with DOIs

\leavevmode\hypertarget{ref-Blackwood2010}{}%
Blackwood, J. C., A. Hastings, and C. Costello. 2010. Cost-effective
management of invasive species using linear-quadratic control.
Ecological Economics 69:519--527.

\leavevmode\hypertarget{ref-Boettiger2015}{}%
Boettiger, C., M. Mangel, and S. Munch. 2015. Avoiding tipping points in
fisheries management through Gaussian process dynamic programming.
Proceedings of the Royal Society B: Biological Sciences
282:20141631--20141631.

\leavevmode\hypertarget{ref-pomdp-intro}{}%
Boettiger, C., and M. Memarzadeh. 2018. Supplement to: "Resolving the
measurement uncertainty paradox in ecological management". Zenodo.

\leavevmode\hypertarget{ref-sarsop-pkg}{}%
Boettiger, C., J. Ooms, and M. Memarzadeh. 2018. sarsop: Approximate
POMDP Planning Software in R, v0.5.0,
\textless{}https://github.com/boettiger-lab/sarsop\textgreater{}.

@@

\leavevmode\hypertarget{ref-Britten2017}{}%
Britten, G. L., M. Dowd, L. Kanary, and B. Worm. 2017. Extended
fisheries recovery timelines in a changing environment. Nature
Communications 8:15325.

@@

\leavevmode\hypertarget{ref-Chades2011}{}%
Chadès, I., T. G. Martin, S. Nicol, M. A. Burgman, H. P. Possingham, and
Y. M. Buckley. 2011. General rules for managing and surveying networks
of pests, diseases, and endangered species. Proceedings of the National
Academy of Sciences 108:8323--8.

\leavevmode\hypertarget{ref-Chades2008}{}%
Chadès, I., E. McDonald-Madden, M. a McCarthy, B. Wintle, M. Linkie, and
H. P. Possingham. 2008. When to stop managing or surveying cryptic
threatened species. Proceedings of the National Academy of Sciences
105:13936--40.

\leavevmode\hypertarget{ref-Clark1973}{}%
Clark, C. W. 1973. Profit maximization and the extinction of animal
species. Journal of Political Economy 81:950--961.

@@

\leavevmode\hypertarget{ref-Clark1986}{}%
Clark, C. W., and G. P. Kirkwood. 1986. On uncertain renewable resource
stocks: Optimal harvest policies and the value of stock surveys. Journal
of Environmental Economics and Management 13:235--244.

\leavevmode\hypertarget{ref-Costello2016}{}%
Costello, C., D. Ovando, T. Clavelle, C. K. Strauss, R. Hilborn, M. C.
Melnychuk, T. A. Branch, et al. 2016. Global fishery prospects under
contrasting management regimes. Proceedings of the National Academy of
Sciences 113:5125--5129.

\leavevmode\hypertarget{ref-Dee2017}{}%
Dee, L. E., M. De Lara, C. Costello, and S. D. Gaines. 2017. To what
extent can ecosystem services motivate protecting biodiversity? Ecology
Letters 20:935--946.

\leavevmode\hypertarget{ref-nimble}{}%
de Valpine, P., D. Turek, C. J. Paciorek, C. Anderson-Bergman, T.
Duncan, and R. Bodik. 2017. Programming With Models: Writing Statistical
Algorithms for General Model Structures With NIMBLE. Journal of
Computational and Graphical Statistics 26:403--413.

\leavevmode\hypertarget{ref-Dichmont2016}{}%
Dichmont, C. M., R. A. Deng, A. E. Punt, J. Brodziak, Y.-J. Chang, J. M.
Cope, J. N. Ianelli, et al. 2016. A review of stock assessment packages
in the united states. Fisheries Research 183:447--460.

\leavevmode\hypertarget{ref-Dorner2009}{}%
Dorner, B., R. M. Peterman, and Z. Su. 2009. Evaluation of performance
of alternative management models of Pacific salmon (Oncorhynchus spp.)
in the presence of climatic change and outcome uncertainty using Monte
Carlo simulations. Canadian Journal of Fisheries and Aquatic Sciences
66:2199--2221.

\leavevmode\hypertarget{ref-Ellison2004}{}%
Ellison, A. M. 2004. Bayesian inference in ecology. Ecology Letters
7:509--520.

@@

\leavevmode\hypertarget{ref-Fischer2009}{}%
Fischer, J., G. D. Peterson, T. a Gardner, L. J. Gordon, I. Fazey, T.
Elmqvist, A. Felton, et al. 2009. Integrating resilience thinking and
optimisation for conservation. Trends in ecology \& evolution
24:549--54.

\leavevmode\hypertarget{ref-Gordon1954}{}%
Gordon, H. S., and C. Press. 1954. The Economic Theory of a
Common-Property Resource: The Fishery. Journal of Political Economy
62:124--142.

\leavevmode\hypertarget{ref-Halpern2013}{}%
Halpern, B. S., C. J. Klein, C. J. Brown, M. Beger, H. S. Grantham, S.
Mangubhai, M. Ruckelshaus, et al. 2013. Achieving the triple bottom line
in the face of inherent trade-offs among social equity, economic return,
and conservation. Proceedings of the National Academy of Sciences
110:6229--34.

@@

\leavevmode\hypertarget{ref-Holling1973}{}%
Holling, C. S. 1973. Resilience and Stability of Ecological Systems.
Annual Review of Ecology and Systematics 4:1--23.

\leavevmode\hypertarget{ref-Iacona2017}{}%
Iacona, G. D., H. P. Possingham, and M. Bode. 2017. Waiting can be an
optimal conservation strategy, even in a crisis discipline. Proceedings
of the National Academy of Sciences 114:201702111.

\leavevmode\hypertarget{ref-Johnson2015}{}%
Johnson, F. A., and B. K. Williams. 2015. A Decision-Analytic Approach
to Adaptive Resource Management. Pages 61--84 \emph{in} C. R. Allen and
A. S. Garmestani, eds. Adaptive management of social-ecological systems.
Springer Netherlands, Dordrecht.

\leavevmode\hypertarget{ref-Kaelbling1998}{}%
Kaelbling, L. P., M. L. Littman, and A. R. Cassandra. 1998. Planning and
Acting in Partially Observable Stochastic Domains. Artificial
Intelligence 101:99--134.

\leavevmode\hypertarget{ref-Kriebel2001}{}%
Kriebel, D., J. Tickner, P. Epstein, J. Lemons, R. Levins, E. L.
Loechler, M. Quinn, et al. 2001. The precautionary principle in
environmental science. Environmental health perspectives 109:871--6.

@@

\leavevmode\hypertarget{ref-Larkin1977}{}%
Larkin, P. a. 1977. An Epitaph for the Concept of Maximum Sustained
Yield. Transactions of the American Fisheries Society 106:1--11.

\leavevmode\hypertarget{ref-Levin2008}{}%
Levin, S. A., and J. Lubchenco. 2008. Resilience, Robustness, and Marine
Ecosystem-based Management. BioScience 58:27--32.

\leavevmode\hypertarget{ref-Li2017}{}%
Li, S.-L., O. N. Bjørnstad, M. J. Ferrari, R. Mummah, M. C. Runge, C. J.
Fonnesbeck, M. J. Tildesley, et al. 2017. Essential information:
Uncertainty and optimal control of Ebola outbreaks. Proceedings of the
National Academy of Sciences 114:5659--5664.

@@

\leavevmode\hypertarget{ref-Ludwig1982}{}%
Ludwig, D., and C. J. Walters. 1982. Optimal harvesting with imprecise
parameter estimates. Ecological Modelling 14:273--292.

\leavevmode\hypertarget{ref-Mace2001}{}%
Mace, P. M. 2001. A new role for MSY in single-species and ecosystem
approaches to fisheries stock assessment and management. Fish and
Fisheries 2:2--32.

@@

\leavevmode\hypertarget{ref-Marescot2013}{}%
Marescot, L., G. Chapron, I. Chadès, P. L. Fackler, C. Duchamp, E.
Marboutin, and O. Gimenez. 2013. Complex decisions made simple: a primer
on stochastic dynamic programming. Methods in Ecology and Evolution
4:872--884.

\leavevmode\hypertarget{ref-Marwick2018}{}%
Marwick, B., C. Boettiger, and L. Mullen. 2018. Packaging Data
Analytical Work Reproducibly Using R (and Friends). The American
Statistician 72:80--88.

\leavevmode\hypertarget{ref-May1977}{}%
May, R. M. 1977. Thresholds and breakpoints in ecosystems with a
multiplicity of stable states. Nature 269:471--477.

\leavevmode\hypertarget{ref-Memarzadeh2018}{}%
Memarzadeh, M., and C. Boettiger. 2018. Adaptive management of
ecological systems under partial observability. Biological Conservation
224:9--15.

@@

\leavevmode\hypertarget{ref-Nicol2011}{}%
Nicol, S., and I. Chadès. 2011. Beyond stochastic dynamic programming: a
heuristic sampling method for optimizing conservation decisions in very
large state spaces. Methods in Ecology and Evolution 2:221--228.

@@

\leavevmode\hypertarget{ref-Petchy2015}{}%
Petchey, O. L., M. Pontarp, T. M. Massie, S. Kéfi, A. Ozgul, M.
Weilenmann, G. M. Palamara, et al. 2015. The ecological forecast
horizon, and examples of its uses and determinants. Ecology Letters
18:597--611.

@@

\leavevmode\hypertarget{ref-Polasky2011}{}%
Polasky, S., S. R. Carpenter, C. Folke, and B. Keeler. 2011.
Decision-making under great uncertainty: environmental management in an
era of global change. Trends in Ecology \& Evolution 26:398--404.

\leavevmode\hypertarget{ref-Punt2016}{}%
Punt, A. E., D. S. Butterworth, C. L. de Moor, J. A. A. De Oliveira, and
M. Haddon. 2016. Management strategy evaluation: best practices. Fish
and Fisheries 17:303--334.

@@

\leavevmode\hypertarget{ref-Reed1979}{}%
Reed, W. J. 1979. Optimal escapement levels in stochastic and
deterministic harvesting models. Journal of Environmental Economics and
Management 6:350--363.

@@

\leavevmode\hypertarget{ref-Richards1999}{}%
Richards, S. A., H. P. Possingham, and J. Tizard. 1999. Optimal Fire
Management for Maintaining Community Diversity. Ecological Applications
9:880--892.

@@

\leavevmode\hypertarget{ref-Schaefer1954}{}%
Schaefer, M. B. 1954. Some aspects of the dynamics of populations
important to the management of the commercial marine fisheries. Bulletin
of the Inter-American Tropical Tuna Commission 1:27--56.

\leavevmode\hypertarget{ref-Sethi2005}{}%
Sethi, G., C. Costello, A. Fisher, M. Hanemann, and L. Karp. 2005.
Fishery management under multiple uncertainty. Journal of Environmental
Economics and Management 50:300--318.

\leavevmode\hypertarget{ref-Shea1998}{}%
Shea, K. 1998. Management of populations in conservation, harvesting and
control. Trends in Ecology and Evolution 13:371--375.

\leavevmode\hypertarget{ref-Shea2014}{}%
Shea, K., M. J. Tildesley, M. C. Runge, C. J. Fonnesbeck, and M. J.
Ferrari. 2014. Adaptive Management and the Value of Information:
Learning Via Intervention in Epidemiology. PLoS Biology 12:9--12.

@@

\leavevmode\hypertarget{ref-Walters1976}{}%
Walters, C. J., and R. Hilborn. 1976. Adaptive Control of Fishing
Systems. Journal of the Fisheries Research Board of Canada 33:145--159.

\leavevmode\hypertarget{ref-Walters1978}{}%
---------. 1978. Ecological Optimization and Adaptive Management. Annual
Review of Ecology and Systematics 9:157--188.

\leavevmode\hypertarget{ref-Weitzman2002}{}%
Weitzman, M. L. 2002. Landing Fees vs Harvest Quotas with Uncertain Fish
Stocks. Journal of Environmental Economics and Management 43:325--338.

\leavevmode\hypertarget{ref-Williams2001}{}%
Williams, B. K. 2001. Uncertainty , learning , and the optimal
management of wildlife. Environmental and Ecological Statistics
8:269--288.

\leavevmode\hypertarget{ref-Williams2011}{}%
---------. 2011. Resolving structural uncertainty in natural resources
management using POMDP approaches. Ecological Modelling 222:1092--1102.

>>>>

\leavevmode\hypertarget{ref-Blackwood2010}{}%
Blackwood, J. C., A. Hastings, and C. Costello. 2010. Cost-effective
management of invasive species using linear-quadratic control.
Ecological Economics 69:519--527.
DOI:\href{https://doi.org/10.1016/j.ecolecon.2009.08.029}{10.1016/j.ecolecon.2009.08.029}.

\leavevmode\hypertarget{ref-Boettiger2015}{}%
Boettiger, C., M. Mangel, and S. Munch. 2015. Avoiding tipping points in
fisheries management through Gaussian process dynamic programming.
Proceedings of the Royal Society B: Biological Sciences
282:20141631--20141631.
DOI:\href{https://doi.org/10.1098/rspb.2014.1631}{10.1098/rspb.2014.1631}.

\leavevmode\hypertarget{ref-pomdp-intro}{}%
Boettiger, C., and M. Memarzadeh. 2018. Supplement to: "Resolving the
measurement uncertainty paradox in ecological management". Zenodo,
DOI:\href{https://doi.org/10.5281/zenodo.2528507}{10.5281/zenodo.2528507}.

\leavevmode\hypertarget{ref-sarsop-pkg}{}%
Boettiger, C., J. Ooms, and M. Memarzadeh. 2018. sarsop: Approximate
POMDP Planning Software in R, v0.5.0,
\textless{}https://github.com/boettiger-lab/sarsop\textgreater{}.
DOI:\href{https://doi.org/10.5281/zenodo.1162856}{10.5281/zenodo.1162856}.

@@

\leavevmode\hypertarget{ref-Britten2017}{}%
Britten, G. L., M. Dowd, L. Kanary, and B. Worm. 2017. Extended
fisheries recovery timelines in a changing environment. Nature
Communications 8:15325.
DOI:\href{https://doi.org/10.1038/ncomms15325}{10.1038/ncomms15325}.

@@

\leavevmode\hypertarget{ref-Chades2011}{}%
Chadès, I., T. G. Martin, S. Nicol, M. A. Burgman, H. P. Possingham, and
Y. M. Buckley. 2011. General rules for managing and surveying networks
of pests, diseases, and endangered species. Proceedings of the National
Academy of Sciences 108:8323--8.
DOI:\href{https://doi.org/10.1073/pnas.1016846108}{10.1073/pnas.1016846108}.

\leavevmode\hypertarget{ref-Chades2008}{}%
Chadès, I., E. McDonald-Madden, M. a McCarthy, B. Wintle, M. Linkie, and
H. P. Possingham. 2008. When to stop managing or surveying cryptic
threatened species. Proceedings of the National Academy of Sciences
105:13936--40.
DOI:\href{https://doi.org/10.1073/pnas.0805265105}{10.1073/pnas.0805265105}.

\leavevmode\hypertarget{ref-Clark1973}{}%
Clark, C. W. 1973. Profit maximization and the extinction of animal
species. Journal of Political Economy 81:950--961.
DOI:\href{https://doi.org/10.1086/260090}{10.1086/260090}.

@@

\leavevmode\hypertarget{ref-Clark1986}{}%
Clark, C. W., and G. P. Kirkwood. 1986. On uncertain renewable resource
stocks: Optimal harvest policies and the value of stock surveys. Journal
of Environmental Economics and Management 13:235--244.
DOI:\href{https://doi.org/10.1016/0095-0696(86)90024-0}{10.1016/0095-0696(86)90024-0}.

\leavevmode\hypertarget{ref-Costello2016}{}%
Costello, C., D. Ovando, T. Clavelle, C. K. Strauss, R. Hilborn, M. C.
Melnychuk, T. A. Branch, et al. 2016. Global fishery prospects under
contrasting management regimes. Proceedings of the National Academy of
Sciences 113:5125--5129.
DOI:\href{https://doi.org/10.1073/pnas.1520420113}{10.1073/pnas.1520420113}.

\leavevmode\hypertarget{ref-Dee2017}{}%
Dee, L. E., M. De Lara, C. Costello, and S. D. Gaines. 2017. To what
extent can ecosystem services motivate protecting biodiversity? Ecology
Letters 20:935--946.
DOI:\href{https://doi.org/10.1111/ele.12790}{10.1111/ele.12790}.

\leavevmode\hypertarget{ref-nimble}{}%
de Valpine, P., D. Turek, C. J. Paciorek, C. Anderson-Bergman, T.
Duncan, and R. Bodik. 2017. Programming With Models: Writing Statistical
Algorithms for General Model Structures With NIMBLE. Journal of
Computational and Graphical Statistics 26:403--413.
DOI:\href{https://doi.org/10.1080/10618600.2016.1172487}{10.1080/10618600.2016.1172487}.

\leavevmode\hypertarget{ref-Dichmont2016}{}%
Dichmont, C. M., R. A. Deng, A. E. Punt, J. Brodziak, Y.-J. Chang, J. M.
Cope, J. N. Ianelli, et al. 2016. A review of stock assessment packages
in the united states. Fisheries Research 183:447--460.
DOI:\href{https://doi.org/10.1016/j.fishres.2016.07.001}{10.1016/j.fishres.2016.07.001}.

\leavevmode\hypertarget{ref-Dorner2009}{}%
Dorner, B., R. M. Peterman, and Z. Su. 2009. Evaluation of performance
of alternative management models of Pacific salmon (Oncorhynchus spp.)
in the presence of climatic change and outcome uncertainty using Monte
Carlo simulations. Canadian Journal of Fisheries and Aquatic Sciences
66:2199--2221.
DOI:\href{https://doi.org/10.1139/F09-144}{10.1139/F09-144}.

\leavevmode\hypertarget{ref-Ellison2004}{}%
Ellison, A. M. 2004. Bayesian inference in ecology. Ecology Letters
7:509--520.
DOI:\href{https://doi.org/10.1111/j.1461-0248.2004.00603.x}{10.1111/j.1461-0248.2004.00603.x}.

@@

\leavevmode\hypertarget{ref-Fischer2009}{}%
Fischer, J., G. D. Peterson, T. a Gardner, L. J. Gordon, I. Fazey, T.
Elmqvist, A. Felton, et al. 2009. Integrating resilience thinking and
optimisation for conservation. Trends in ecology \& evolution
24:549--54.
DOI:\href{https://doi.org/10.1016/j.tree.2009.03.020}{10.1016/j.tree.2009.03.020}.

\leavevmode\hypertarget{ref-Gordon1954}{}%
Gordon, H. S., and C. Press. 1954. The Economic Theory of a
Common-Property Resource: The Fishery. Journal of Political Economy
62:124--142. DOI:\href{https://doi.org/10.1086/257497}{10.1086/257497}.

\leavevmode\hypertarget{ref-Halpern2013}{}%
Halpern, B. S., C. J. Klein, C. J. Brown, M. Beger, H. S. Grantham, S.
Mangubhai, M. Ruckelshaus, et al. 2013. Achieving the triple bottom line
in the face of inherent trade-offs among social equity, economic return,
and conservation. Proceedings of the National Academy of Sciences
110:6229--34.
DOI:\href{https://doi.org/10.1073/pnas.1217689110}{10.1073/pnas.1217689110}.

@@

\leavevmode\hypertarget{ref-Holling1973}{}%
Holling, C. S. 1973. Resilience and Stability of Ecological Systems.
Annual Review of Ecology and Systematics 4:1--23.
DOI:\href{https://doi.org/10.1146/annurev.es.04.110173.000245}{10.1146/annurev.es.04.110173.000245}.

\leavevmode\hypertarget{ref-Iacona2017}{}%
Iacona, G. D., H. P. Possingham, and M. Bode. 2017. Waiting can be an
optimal conservation strategy, even in a crisis discipline. Proceedings
of the National Academy of Sciences 114:201702111.
DOI:\href{https://doi.org/10.1073/pnas.1702111114}{10.1073/pnas.1702111114}.

\leavevmode\hypertarget{ref-Johnson2015}{}%
Johnson, F. A., and B. K. Williams. 2015. A Decision-Analytic Approach
to Adaptive Resource Management. Pages 61--84 \emph{in} C. R. Allen and
A. S. Garmestani, eds. Adaptive management of social-ecological systems.
Springer Netherlands, Dordrecht,
DOI:\href{https://doi.org/10.1007/978-94-017-9682-8_5}{10.1007/978-94-017-9682-8\_5}.

\leavevmode\hypertarget{ref-Kaelbling1998}{}%
Kaelbling, L. P., M. L. Littman, and A. R. Cassandra. 1998. Planning and
Acting in Partially Observable Stochastic Domains. Artificial
Intelligence 101:99--134.
DOI:\href{https://doi.org/10.1016/S0004-3702(98)00023-X}{10.1016/S0004-3702(98)00023-X}.

\leavevmode\hypertarget{ref-Kriebel2001}{}%
Kriebel, D., J. Tickner, P. Epstein, J. Lemons, R. Levins, E. L.
Loechler, M. Quinn, et al. 2001. The precautionary principle in
environmental science. Environmental health perspectives 109:871--6.
DOI:\href{https://doi.org/10.2307/3454986}{10.2307/3454986}.

@@

\leavevmode\hypertarget{ref-Larkin1977}{}%
Larkin, P. a. 1977. An Epitaph for the Concept of Maximum Sustained
Yield. Transactions of the American Fisheries Society 106:1--11.
DOI:\href{https://doi.org/10.1577/1548-8659(1977)106\%3C1:AEFTCO\%3E2.0.CO;2}{10.1577/1548-8659(1977)106\textless{}1:AEFTCO\textgreater{}2.0.CO;2}.

\leavevmode\hypertarget{ref-Levin2008}{}%
Levin, S. A., and J. Lubchenco. 2008. Resilience, Robustness, and Marine
Ecosystem-based Management. BioScience 58:27--32.
DOI:\href{https://doi.org/10.1641/B580107}{10.1641/B580107}.

\leavevmode\hypertarget{ref-Li2017}{}%
Li, S.-L., O. N. Bjørnstad, M. J. Ferrari, R. Mummah, M. C. Runge, C. J.
Fonnesbeck, M. J. Tildesley, et al. 2017. Essential information:
Uncertainty and optimal control of Ebola outbreaks. Proceedings of the
National Academy of Sciences 114:5659--5664.
DOI:\href{https://doi.org/10.1073/pnas.1617482114}{10.1073/pnas.1617482114}.

@@

\leavevmode\hypertarget{ref-Ludwig1982}{}%
Ludwig, D., and C. J. Walters. 1982. Optimal harvesting with imprecise
parameter estimates. Ecological Modelling 14:273--292.
DOI:\href{https://doi.org/10.1016/0304-3800(82)90023-0}{10.1016/0304-3800(82)90023-0}.

\leavevmode\hypertarget{ref-Mace2001}{}%
Mace, P. M. 2001. A new role for MSY in single-species and ecosystem
approaches to fisheries stock assessment and management. Fish and
Fisheries 2:2--32.
DOI:\href{https://doi.org/10.1046/j.1467-2979.2001.00033.x}{10.1046/j.1467-2979.2001.00033.x}.

@@

\leavevmode\hypertarget{ref-Marescot2013}{}%
Marescot, L., G. Chapron, I. Chadès, P. L. Fackler, C. Duchamp, E.
Marboutin, and O. Gimenez. 2013. Complex decisions made simple: a primer
on stochastic dynamic programming. Methods in Ecology and Evolution
4:872--884.
DOI:\href{https://doi.org/10.1111/2041-210X.12082}{10.1111/2041-210X.12082}.

\leavevmode\hypertarget{ref-Marwick2018}{}%
Marwick, B., C. Boettiger, and L. Mullen. 2018. Packaging Data
Analytical Work Reproducibly Using R (and Friends). The American
Statistician 72:80--88.
DOI:\href{https://doi.org/10.1080/00031305.2017.1375986}{10.1080/00031305.2017.1375986}.

\leavevmode\hypertarget{ref-May1977}{}%
May, R. M. 1977. Thresholds and breakpoints in ecosystems with a
multiplicity of stable states. Nature 269:471--477.
DOI:\href{https://doi.org/10.1038/269471a0}{10.1038/269471a0}.

\leavevmode\hypertarget{ref-Memarzadeh2018}{}%
Memarzadeh, M., and C. Boettiger. 2018. Adaptive management of
ecological systems under partial observability. Biological Conservation
224:9--15.
DOI:\href{https://doi.org/10.1016/j.biocon.2018.05.009}{10.1016/j.biocon.2018.05.009}.

@@

\leavevmode\hypertarget{ref-Nicol2011}{}%
Nicol, S., and I. Chadès. 2011. Beyond stochastic dynamic programming: a
heuristic sampling method for optimizing conservation decisions in very
large state spaces. Methods in Ecology and Evolution 2:221--228.
DOI:\href{https://doi.org/10.1111/j.2041-210X.2010.00069.x}{10.1111/j.2041-210X.2010.00069.x}.

@@

\leavevmode\hypertarget{ref-Petchy2015}{}%
Petchey, O. L., M. Pontarp, T. M. Massie, S. Kéfi, A. Ozgul, M.
Weilenmann, G. M. Palamara, et al. 2015. The ecological forecast
horizon, and examples of its uses and determinants. Ecology Letters
18:597--611.
DOI:\href{https://doi.org/10.1111/ele.12443}{10.1111/ele.12443}.

@@

\leavevmode\hypertarget{ref-Polasky2011}{}%
Polasky, S., S. R. Carpenter, C. Folke, and B. Keeler. 2011.
Decision-making under great uncertainty: environmental management in an
era of global change. Trends in Ecology \& Evolution 26:398--404.
DOI:\href{https://doi.org/10.1016/j.tree.2011.04.007}{10.1016/j.tree.2011.04.007}.

\leavevmode\hypertarget{ref-Punt2016}{}%
Punt, A. E., D. S. Butterworth, C. L. de Moor, J. A. A. De Oliveira, and
M. Haddon. 2016. Management strategy evaluation: best practices. Fish
and Fisheries 17:303--334.
DOI:\href{https://doi.org/10.1111/faf.12104}{10.1111/faf.12104}.

@@

\leavevmode\hypertarget{ref-Reed1979}{}%
Reed, W. J. 1979. Optimal escapement levels in stochastic and
deterministic harvesting models. Journal of Environmental Economics and
Management 6:350--363.
DOI:\href{https://doi.org/10.1016/0095-0696(79)90014-7}{10.1016/0095-0696(79)90014-7}.

@@

\leavevmode\hypertarget{ref-Richards1999}{}%
Richards, S. A., H. P. Possingham, and J. Tizard. 1999. Optimal Fire
Management for Maintaining Community Diversity. Ecological Applications
9:880--892.
DOI:\href{https://doi.org/10.1890/1051-0761(1999)009\%5B0880:OFMFMC\%5D2.0.CO;2}{10.1890/1051-0761(1999)009{[}0880:OFMFMC{]}2.0.CO;2}.

@@

\leavevmode\hypertarget{ref-Schaefer1954}{}%
Schaefer, M. B. 1954. Some aspects of the dynamics of populations
important to the management of the commercial marine fisheries. Bulletin
of the Inter-American Tropical Tuna Commission 1:27--56.
DOI:\href{https://doi.org/10.1007/BF02464432}{10.1007/BF02464432}.

\leavevmode\hypertarget{ref-Sethi2005}{}%
Sethi, G., C. Costello, A. Fisher, M. Hanemann, and L. Karp. 2005.
Fishery management under multiple uncertainty. Journal of Environmental
Economics and Management 50:300--318.
DOI:\href{https://doi.org/10.1016/j.jeem.2004.11.005}{10.1016/j.jeem.2004.11.005}.

\leavevmode\hypertarget{ref-Shea1998}{}%
Shea, K. 1998. Management of populations in conservation, harvesting and
control. Trends in Ecology and Evolution 13:371--375.
DOI:\href{https://doi.org/10.1016/S0169-5347(98)01381-0}{10.1016/S0169-5347(98)01381-0}.

\leavevmode\hypertarget{ref-Shea2014}{}%
Shea, K., M. J. Tildesley, M. C. Runge, C. J. Fonnesbeck, and M. J.
Ferrari. 2014. Adaptive Management and the Value of Information:
Learning Via Intervention in Epidemiology. PLoS Biology 12:9--12.
DOI:\href{https://doi.org/10.1371/journal.pbio.1001970}{10.1371/journal.pbio.1001970}.

@@

\leavevmode\hypertarget{ref-Walters1976}{}%
Walters, C. J., and R. Hilborn. 1976. Adaptive Control of Fishing
Systems. Journal of the Fisheries Research Board of Canada 33:145--159.
DOI:\href{https://doi.org/10.1139/f76-017}{10.1139/f76-017}.

\leavevmode\hypertarget{ref-Walters1978}{}%
---------. 1978. Ecological Optimization and Adaptive Management. Annual
Review of Ecology and Systematics 9:157--188.
DOI:\href{https://doi.org/10.1146/annurev.es.09.110178.001105}{10.1146/annurev.es.09.110178.001105}.

\leavevmode\hypertarget{ref-Weitzman2002}{}%
Weitzman, M. L. 2002. Landing Fees vs Harvest Quotas with Uncertain Fish
Stocks. Journal of Environmental Economics and Management 43:325--338.
DOI:\href{https://doi.org/10.1006/jeem.2000.1181}{10.1006/jeem.2000.1181}.

\leavevmode\hypertarget{ref-Williams2001}{}%
Williams, B. K. 2001. Uncertainty , learning , and the optimal
management of wildlife. Environmental and Ecological Statistics
8:269--288.
DOI:\href{https://doi.org/10.1023/A:1011395725123}{10.1023/A:1011395725123}.

\leavevmode\hypertarget{ref-Williams2011}{}%
---------. 2011. Resolving structural uncertainty in natural resources
management using POMDP approaches. Ecological Modelling 222:1092--1102.
DOI:\href{https://doi.org/10.1016/j.ecolmodel.2010.12.015}{10.1016/j.ecolmodel.2010.12.015}.
